Hillary Clinton Emails

### 2016-04-14 presentation/presentation.tex
Minor changes.
add multinomial regression

>>>>

\begin{frame}{Conclusion}
\begin{itemize}
\item We've broken the corpus down to a level where we can effectively analyze it and draw conclusions using both human and statistical analysis
\item This has only been a sample of the many questions we could address using the LDA output
\item Possible future directions
  \begin{itemize}
  \item Some emails are redacted, how do email topics relate to this
  \item Correlation between topics, what topics appear together
  \item Predicting senders or receivers based on email text
  \end{itemize}
\end{itemize}
\end{frame}
